Quantitative processing of broadband data as implemented in a scientific splitbeam echosounder

### 2023-09-19 Paper/Manuscript.tex
Updated manuscript

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram_m_n}
\caption{\label{fi:Fig_Sv_echogram} Illustration of volume backscattering strength as a function of frequency, Sv(f). A non-swimbladdered fish school is seen as a registration between 15 and 35 m range, and the sea floor is seen at approximately 50 m. (a) Sv as a function of ping number and range range for the raw data file used in the Sv(f) example. The red vertical line indicates the ping that is used for illustrating the Sv(f) processing used in (b). (b) Sv(f) as a function of frequency and range for a single ping indicated in (a) with a vertical red line.}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=16cm]{Fig_Sv_echogram_m_n}
\caption{\label{fi:Fig_Sv_echogram} Illustration of volume backscattering strength as a function of frequency, Sv(f). A non-swimbladdered fish school is seen as a registration between 15 and 35 m range, and the sea floor is seen at approximately 50 m. (a) Sv as a function of ping number and range range for the raw data file used in the Sv(f) example. The red vertical line indicates the ping that is used for illustrating the Sv(f) processing used in (b). (b) Sv(f) as a function of frequency and range for a single ping indicated in (a) with a vertical red line. In this example the decimated sampling rate ($\fsdec$, Eq. \ref{eq:fsdec}) is 93.75 kHz, the nominal pulse duration ($\tnom$) is 2 ms, and the effective pulse duration ($\teff$, Eq. \ref{eq:TauEff}) is 0.02 ms.}
\end{figure}
